
\section{Publications}

\subsection{Peer-reviewed publications}

\text{\textbf{Girons Lopez, M.}, Seibert, J. (2016). Influence of Hydro-Meteorological Data Spatial Aggregation on Streamflow Modelling. \textit{Journal of Hydrology, 541}, 1212-1220. doi:\href{http://www.sciencedirect.com/science/article/pii/S0022169416305170}{10.1016/j.jhydrol.2016.08.026}}

\text{\textbf{Girons Lopez, M.}, Wennerstr\"{o}m, H., Nord\'{e}n, L.-\r{A}., Seibert, J. (2015) Location and density of Rain Gauges for the Estimation of Spatial Varying Precipitation. \textit{Geografiska Annaler. Series A, Physical Geography, 97}, 167-179. doi:\href{http://onlinelibrary.wiley.com/doi/10.1111/geoa.12094}{10.1111/geoa.12094}}

\subsection{Manuscripts under preparation}

\text{\textbf{Girons Lopez, M.}, Di Baldassarre, G., Seibert, J. (2016). Assessing the Impact of Social Memory on Flood Early Warning Systems. \textit{Manuscript under review}.}

\text{Rivera, S., \textbf{Girons Lopez, M.}, Seibert, J., Minsker, B. (2016). Probabilistic Flood Mapping Using Volunteered Geographical Information. \textit{Manuscript under preparation}.}

\subsection{Theses}

\text{\textbf{Girons Lopez, M.} (2016) Information Needs for Water Resource and Risk Management: Hydro-Meteorological Data Value and Non-Traditional Information \textit{PhD Thesis, Uppsala University, Sweden}. ISBN:\href{http://www.diva-portal.org/smash/record.jsf?pid=diva2\%3A957429\&dswid=-4195}{978-91-554-9679-1}}

\text{\textbf{Girons Lopez, M.} (2011) Modelling Climatic and Hydrological Variability in Lake Babati, Northern Tanzania. \textit{Master Thesis, Stockholm University, Sweden}. OAI:\href{http://www.diva-portal.org/smash/record.jsf?pid=diva2\%3A788849\&dswid=\_new}{DiVA.org:su-114009}}

\subsection{Conference contributions}

\text{\textbf{Girons Lopez, M.}, Di Baldassarre, G., Seibert, J. (2016) Impact of Social Memory on the Efficiency of Flood Early Warning Systems (FEWS). \textit{13th Congress INTERPRAEVENT 2016, Lucerne, Switzerland}.}

\text{\textbf{Girons Lopez, M.}, Di Baldassarre, G., Grabs, T., Halldin, S., Seibert, J. (2016) Exploring the Role of Social Memory of Floods for Designing Flood Early Warning Operations. \textit{EGU General Assembly, Vienna, Austria}.}

\text{Rivera, S., \textbf{Girons Lopez, M.}, Minsker, B., Seibert, J. (2015) Probabilistic Flood Mapping using Volunteered Geographical Information. \textit{3rd CUAHSI Conference on Hydroinformatics, Tuscaloosa, Alabama}.}

\text{\textbf{Girons Lopez, M.}, Seibert, J., Halldin, S., Wennerstr\"{o}m, H. (2013) Value of distributed precipitation for flood early warning: A case study for a pre-alpine catchment in Switzerland. \textit{Knowledge for the Future - Joint IAHS-IAPSO-IASPEI Assembly, Gothenburg, Sweden}.}

\text{Mbanguka, R. P., \textbf{Girons Lopez, M.}, Jarsj\"{o}, J. (2013) A Water Balance Model for Assessing Hydro Climatic Variability in Tropical Lake Systems: Application to Lake Babati and Lake Emakat, Northern Tanzania. \textit{EGU General Assembly, Vienna, Austria}.}

\sectionsep