
\section{Teaching}

\subsection{Training}

\text{\textbf{2015} \hspace{10mm} \textbf{Academic Teacher Training Course II}}\\
\text{\hspace{19mm} Uppsala University, Uppsala (Sweden)}

\subsection{Instructor}

\text{\textbf{Climate and Landscape}\\
	Uppsala University, Spring 2013\\
	\textit{Taught the part of the course related with water in the landscape}}

\text{\textbf{Hydrology and Water Resource Management}\\
	Uppsala University, Autumn 2012 - 2016\\
	\textit{Taught the part of the course related with atmospheric water, led field runoff measurements and a water balance estimation project, constructed and graded exams.}}

\text{\textbf{Field Methods in Earth Science}\\
	Uppsala University, Spring 2015 - 2016\\
	\textit{Taught how to use data loggers for environmental modelling and led a project on evapotranspiration estimation based on field measurements.}}

\text{\textbf{Groundwater and Surface Water Modelling}\\
	Uppsala University, Spring 2015 - 2016\\
	\textit{Taught the fundaments of hydrological with HBV, led a project on hydrological modelling and held a seminar.}}

\subsection{Teaching Assistant}

\text{\textbf{Meteorology, hydrology and Environmental Measurement Techniques}\\
	Uppsala University, Autumn 2013 - 2016\\
	\textit{Led numerical exercise solving sessions, field measurements of a number of hydrological processes and processing of field data.}}

\text{\textbf{Distribution and Treatment of Drinking Water}\\
	Uppsala University, Autumn 2011 - 2012\\
	\textit{Assisted students during laboratory work, graded exercises and exams.}}

\text{\textbf{GIS for Water Resources}\\
	Uppsala University, Spring 2012 - 2016\\
	\textit{Constructed laboratory instructions and assisted students during laboratory work.}}

\text{\textbf{Runoff}\\
	Uppsala University, Autumn 2012 - 2014\\
	\textit{Assisted students during laboratory work.}}

\text{\textbf{Soil Mechanics and Engineering Geology}\\
	Uppsala University, Autumn 2012 - 2015\\
	\textit{Reviewed concepts of classical mechanics at the beginning of the course and graded exercises.}}

\text{\textbf{Groundwater and Runoff modelling}\\
	Uppsala University, Autumn 2012 - 2014\\
	\textit{Led a project on hydrological modelling using HBV and graded reports.}}

\text{\textbf{Statistical Methods in Hydrology}\\
	Uppsala University, Spring 2012\\
	\textit{Graded exams.}}

\text{\textbf{Snow Physics and Hydrology}\\
	Uppsala University, Fall 2015\\
	\textit{Assisted students during laboratory work.}}

\text{\textbf{Field Course in Earth Science II}\\
	Uppsala University, Spring 2013 - 2014\\
	\textit{Led field measurements of a number of hydrological processes.}}

\text{\textbf{Global Hydrology}\\
	Uppsala University, Autumn 2011\\
	\textit{Led topographic field measurements.}}

\sectionsep