% Girons Lopez - Resume template

\documentclass[]{gironslopez-resume}

\begin{document}

  \noindent

  \lastupdated

  \name{Marc}{Girons Lopez}

  \contact{\href{http://gironslopez.me}{gironslopez.me} \\
    Flogstavägen 81E, SE-752 72 Uppsala \\
    \href{mailto:m.girons@gmail.com}{m.girons@gmail.com} \textbar
    +46 (0)70-712-3280}

  \begin{minipage}[t]{0.33\textwidth}

    \section{Education}

    \subsection{Uppsala University}
    \descript{PhD in Hydrology}
    \location{Expected Oct 2016 \textbar Uppsala, Sweden}
    \text{Using socio-hydrological data for improving water management practices. \\
    Main Supervisor: Jan Seibert}

    \sectionsep

    \subsection{Uppsala University}
    \descript{MSc in Earth Sciences (Hydrology/Hydrogeology)}
    \location{Aug 2009 - Jun 2011 \textbar Uppsala, Sweden}

    \sectionsep

    \subsection{Universitat Aut\`onoma de Barcelona (UAB)}
    \descript{BSc in Geology}
    \location{Sep 2004 - Jun 2009 \textbar Barcelona, Spain}

    \sectionsep

    \subsection{Universit\'e Joseph Fourier (Grenoble 1)}
    \descript{ERASMUS program}
    \location{Sep 2007 - Jun 2008 \textbar Grenoble, France}

    \sectionsep

    \section{Links}
    \text{
    Github:// \href{https://github.com/gironslopez}{\bf GironsLopez} \\
    LinkedIn://  \href{https://www.linkedin.com/in/marcgirons}{\bf marcgirons}
    }

    \sectionsep

    \section{Skills}

    \subsection{Programming}
    \text{Python \textbullet{} Matlab \textbullet{} \LaTeX\ \textbullet{} Fortran}

    \sectionsep

    \subsection{Scientific software}
    \text{ArcGIS \textbullet{} QGIS \textbullet{} HBV}

    \sectionsep

    \subsection{Languages}
    \location{Native}
    \text{Catalan \textbullet{} Spanish}

    \location{Fluent}
    \text{English \textbullet{} French}

    \location{Intermediate}
    \text{Swedish}

    \sectionsep

    \section{Scholarships}

    \text{
    \begin{tabular}{ll}
      2014 & Liljewalchs travel grant \\
      2010 & The Swedish - Spanish \\
      & Foundation for the \\
      & Promotion of Education \\
	    & and Studies scholarship \\
      2007 & ERASMUS scholarship
    \end{tabular}
    }

    \sectionsep

  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.66\textwidth}

    \section{Professional experience}

    \runsubsection{Laboratori Catal\`a de Control}
    \descript{Lab technician intern}
    \location{Jun 2009 – Sep 2009 \textbar Barcelona, Spain}
    \vspace{\topsep}
    \begin{tightemize}
      \item Quality control of soils and construction materials for civil engineering projects as well as water analyses.
      \item Adoption of ISO rules.
    \end{tightemize}

    \sectionsep

    \runsubsection{URS}
    \descript{Consultant intern}
    \location{Jun 2008 – Sep 2008 \textbar Barcelona, Spain}
    \begin{tightemize}
      \item Environmental control tests, soil decontamination and hydro-geological data processing.
      \item Limnology field work for quality control of riverine systems.
    \end{tightemize}

    \sectionsep

    \section{Research}

    \text{
    \textbf{Girons Lopez, M., Di Baldassarre, G., Grabs, T., Halldin, S., Seibert, J.} (2016) \textit{Exploring the Role of Social Memory of Floods for Designing Flood Early Warning Operations}. Poster presented at the EGU General Assembly, Vienna, Austria.

    \textbf{Girons Lopez, M., Wennerstr\"om, H., Nord\'en, L.-\AA ., Seibert, J.} (2015) \textit{Location and density of Rain Gauges for the Estimation of Spatial Varying Precipitation}. Geografiska Annaler. Series A, Physical Geography.

    \textbf{Mbanguka, R. P., Girons Lopez, M., Jarsj\"o, J.} (2013) \textit{A Water Balance Model for Assessing Hydro Climatic Variability In Tropical Lake Systems: Application to Lake Babati and Lake Emakat, Northern Tanzania}. Poster presented at the EGU General Assembly, Vienna, Austria.

    \textbf{Girons Lopez, M.} (2011) \textit{Modelling Climatic and Hydrological Variability in Lake Babati, Northern Tanzania}. Master Thesis, Stockholm University, Sweden.
    }

    \sectionsep

    \section{Teaching Experience}

    \descript{Training}
    \text{
    \begin{tabular}{ll}
      2015 & Academic Teacher Training Course II, Uppsala University, \\
      & Uppsala, Sweden
    \end{tabular}
    }

    \sectionsep

    \descript{Teaching assistant}
    \text{Meteorology, hydrology and Environmental Measurement Techniques \textbullet{} Distribution and Treatment of Drinking Water \textbullet{} GIS for Water Ressources \textbullet{} Runoff \textbullet{} Climate and Landscape \textbullet{} Soil Mechanics and Engineering Geology \textbullet{} Groundwater and Runoff Modelling \textbullet{} Hydrology and Water Resource Management \textbullet{} Statistical Methods in Hydrology}

    \sectionsep

    \descript{Field Work}
    \text{Global Hydrology \textbullet{} Field Course in Earth Science II \textbullet{} Hydrology and Water Resource management}

    \sectionsep

    \section{Representation}

    \text{
    \begin{tabular}{ll}
      2014 & PhD student representative at the Centre for Natural Disaster Science \\
	    & (CNDS) Program Board, Uppsala University, Uppsala, Sweden \\
      2013 & PhD student representative at the Department of Earth Sciences Board, \\
	    & Uppsala University, Uppsala, Sweden \\
      2007 & Student representative at the Geology Section board, Universitat \\
	    & Aut\`onoma de Barcelona, Barcelona, Spain
    \end{tabular}
    }

  \end{minipage}

\end{document}
